Restrictive Clearance Comparison

### 2024-03-21 data-raw/RestrictiveClearance_comparison.Rmd
Update using gas_pbpk for initial comparison. Total clearance for 3 more chemicals-species groups are able to be compared for a total of 36

```{r chems_in_common}
common_chems <- cvt %>%
  subset(analyte_dtxsid %in% get_cheminfo(info = "DTXSID", model = "pbtk")) %>%
  pull(analyte_dtxsid) %>%
  unique()

@@

ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
                         "initial_tkClearance_comparison_httk.png"),
       height = 14,
       width = 5,
       device = "png")
```

>>>>

```{r chems_in_common}
common_chems <- cvt %>%
  subset(analyte_dtxsid %in% get_cheminfo(info = "DTXSID", model = "gas_pbtk")) %>%
  pull(analyte_dtxsid) %>%
  unique()

common_chems[!(common_chems %in% get_cheminfo(info = "DTXSID", model = "pbtk"))] %>% unique() %>% sort()
```

@@

ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
                         "tkClearance_comparison_httk_gasPBPK.png"),
       height = 14,
       width = 5,
       device = "png")
```
